A systematic search for transiting planets in the \KT\ data

### 2015-02-12 ms.tex

The systematics model is a 150-parameter linear combination of PCA components
derived from the full set of 20,000 stellar lightcurves.
That is, it presumes that the systematics afflicting each star are shared in
some way across all other stars.
It is our belief---although not a strict assumption of our model---that these
systematics are caused primarily by pointing drifts, or movements of the
pixels in the focal plane relative to the stars.
In principle, if the systematics \emph{are} dominated by pointing issues, the
systematics model could require only three parameters---three Euler
angles---not 150 amplitudes.
However, because (as the pointing drifts) each star sees it's own unique
local patch of flat-field variations, the mapping from pointing drifts to
brightness variations can be extremely non-linear.
Furthermore, because when the pointing is moving fast, there is effectively
a smearing of the point-spread function, there are effects keyed to the
time derivative of the Euler angles as well.
The large number (150) of linear coefficients gives the linear model the
freedom to model complex non-linear behavior; we are trading off parsimony
in parameters with the enormous computational advantages of maintaining
linearity (and therefore also convexity).
The computational advantages of the linear model are three-fold:
Convexity obviates searching in parameter space for alternative modes;
linear least-squares optimization can be performed with simple linear algebra;
given Gaussian uncertainties and uninformative priors, marginalizations over
the linear parameters also reduces to pure linear algebra.

@@

The goal of this \paper\ was to get exoplanet candidates out of the \KT\ pixel-level data,
it was not to generate light curves...
the project does not really produce corrected light curves at all; why not?

This is not the last time the \KT\ data will be searched...
list some deficiencies of this search method
(these might include approximations in the PHIC,
the fact that it deals well with spacecraft systematics but not stellar variability,
and that it isn't sensitive to single transits (which must be common)).

The machine and hand vetting leave much to be desired...
list some deficiencies of the vetting.

Characterization of these candidates can be much improved...
list the things we could know if we had follow-up observations of the stars.

@@

The completeness and false-positive assessment could be vastly improved...
completeness estimates are not as extensive as desired;
there is essentially no estimate of the non-astrophysical false positive rate.

>>>>

The flexible systematics model we employ is a 150-parameter linear combination of PCA components
derived from the full set of 20,000 stellar lightcurves.
That is, it presumes that the systematics afflicting each star are shared in
some way across other stars.
It is our belief---although not a strict assumption of our model---that these
systematics are caused primarily by pointing drifts, or movements of the
pixels in the focal plane relative to the stars.
In principle, if the systematics \emph{are} dominated by pointing issues, the
systematics model could require only three parameters---three Euler
angles---not 150 amplitudes.
However, because (as the pointing drifts) each star sees it's own unique
local patch of flat-field variations, the mapping from pointing drifts to
brightness variations can be extremely non-linear.
Furthermore, because when the pointing is moving fast there is effectively
a smearing of the point-spread function, there are effects keyed to the
time derivative of the Euler angles as well.
The large number (150) of linear coefficients gives the linear model the
freedom to model complex non-linear behavior; we are trading off parsimony
in parameters with the enormous computational advantages of maintaining
linearity (and therefore also convexity).
The computational advantages of the linear model are three-fold:
Convexity obviates searching in parameter space for alternative modes;
linear least-squares optimization can be performed with simple linear algebra;
given Gaussian uncertainties and uninformative priors, marginalizations over
the linear parameters also reduces to pure linear algebra.

The goal of this \paper\ was to get exoplanet candidates out of the
\KT\ pixel-level data, it was \emph{not} to generate light curves.
That is, both the search phase and the characterization phase of the method
are approximations to computations of a likelihood function for the pixel
data telemetered down from the satellite.
We did not generate ``corrected'' or ``pre-search conditioned'' light-curves
at any stage; we simultaneously fit systematics and the signals of interest
to the raw data.
For this reason, there is no sense in which this method ever really
produces corrected light curves.
For us, a systematics-corrected light curve is not really a thing.

@@

@@

This is not the last time the \KT\ data will be searched!
There are many heuristic choices and short-cuts made in this search.
For example, the choice to work at 150 principal components is a choice
driven more by computational feasibility than any model selection or
utility optimization.
The systematics model is good for spacecraft-induced variability, but not
intrinsic stellar variability.
The systematics model has no concept of a physical model of the spacecraft or
the camera; that is, it makes little use of our prior information about how
\KT\ images are generated physically.
The search is performed with a box model and severe approximations are employed
to make it fast.
We don't consider planets (which must be abundant) on periods longer
than those that would leave two transits within the \KT\ Campaign~1
data set.

Most importantly, perhaps, the machine and hand vetting leave much to be desired...
list some deficiencies of the vetting.

The completeness and false-positive assessment could be vastly improved...
completeness estimates are not as extensive as desired;
there is essentially no estimate of the non-astrophysical false positive rate.
(There really is no proposal on the table anywhere for getting a false-positive
rate for the non-astrophysical FPs.)
